\textbf{\sc Deliberative Autonomy for Marine Robotics}

### 2012-01-30 trunk/conclude.tex
updates

A key role that \rx has played and will continue to play is towards
\emph{event response} scenarios. In Section \ref{sec:results} we show
the role Machine Learning (ML) techniques have played thus far in
in-situ plan adaptation. This interaction between Planning and ML we
believe will play a significant role going forward in the general
theme of exploration and discovery. Interpretation of incoming sensor
data to deal with scientific surprise and readapt for opportunistic
science will be critical to dealing with undersampling the
ocean\footnote{Walter Munk has famously stated \emph{``Most of the
    previous century could be called a “century of undersampling”''}
  -- Testimony to the U.S. Commission On Ocean Policy, 18 April
  2002}. Much of what we know of the ocean was derived by exploring in
the blind. We anticipate longer duration robotic vehicles with enough
onboard computational capacity to run deliberative agents such as \rx
make water-column measurements and reliably track and characterize
dynamic features. While our experiments have already shown such
capabilities the exploration Vs. exploitation tradeoff is better
determined when vehicles can make choices over longer time periods
(weeks and months) to study the impacts of bio-geochemical interaction
driven by longer duration physical forcing.

>>>>

A key role that \rx has played and will continue to play is towards
\emph{event response} scenarios. In Section \ref{sec:results} we show
the role Machine Learning (ML) techniques have played thus far in
in-situ plan adaptation. This interaction between Planning and ML we
believe will play a significant role going forward in the general
theme of exploration and discovery. Interpretation of incoming sensor
data to deal with scientific surprise and readapt for opportunistic
science will be critical to dealing with persistent problem of
undersampling the ocean\footnote{Walter Munk of the Scripps Institute
  of Oceanography has famously stated \emph{``Most of the previous
    century could be called a “century of undersampling”''} --
  Testimony to the U.S. Commission On Ocean Policy, 18 April
  2002}. Much of what we know of the ocean was derived by exploring in
the blind. We anticipate longer duration robotic vehicles with enough
onboard computational capacity to run deliberative agents such as \rx
make water-column measurements and reliably track and characterize
dynamic features. While our experiments have already shown such
capabilities the exploration Vs. exploitation tradeoff is better
determined when vehicles can make choices over longer time periods
(weeks and months) to study the impacts of bio-geochemical interaction
driven by longer duration physical forcing.
